General writeup

### 2017-11-30 Latex/general_writeups/general_writeup.tex
cleaned up the FEV tables and general_writeup a bit

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
	\ifdim\lastskip<1.5em \hskip-\lastskip
	\hskip1.5em plus0em minus0.5em \fi \nobreak
	\vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\def \ourFigPath {../} 
\usepackage{subfigure}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

@@

         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}

@@

         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}

@@

         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}

@@

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}

@@

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}

@@

	\input{FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}

@@

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}

@@

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}

@@

\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}

@@

\input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
	\ifdim\lastskip<1.5em \hskip-\lastskip
	\hskip1.5em plus0em minus0.5em \fi \nobreak
	\vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\def \ourFigPath {../../} 
\usepackage{subfigure}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

@@

         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}

@@

         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}

@@

         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}

@@

	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}

@@

	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}

@@

	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}

@@

	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}

@@

	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}

@@

\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}

@@

\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}
